<<<<<<< Updated upstream


```{r commit 3}

test <- tweets %>% 
  count(screen_name) %>%
  arrange(desc(n)) %>%
  slice(1:25) %>%
  mutate(screen_name = fct_reorder(screen_name, n))


ggplot(data = test, aes(x = screen_name, y = n)) +
            geom_bar(stat="identity", width = 0.7, fill = "cornflowerblue") +
            labs(y = "Count", x = "Twitter Screen Name", title = "Most prolific #rstats tweeters", subtitle = "Top 25 screen names displayed",
                 caption = "Data from Mike Kearny, distributed via#tidytuesday") +
            coord_flip()+ 
            theme(panel.grid.major.x = element_line(colour = "grey",size=0.5),
            panel.grid.major.y = element_blank())+
              scale_y_continuous(minor_breaks = seq(1, 30000, 10000))  
            )

```
=======
---
title: "EDLD 610 Lab 1"
author: "Jim Wright; Claire Zhang; Sophie Pychlau; Mike"
date: "1/8/2020"
output: html_document
toc: true
toc_float: true
theme: united 
highlight: zenburn 
---

```{r setup, include=FALSE}
library(rio)
library(here)
library(tidyverse)
library(knitr)
theme_set(theme_minimal())
opts_chunk$set(echo = FALSE,
               fig.width = 6.5,
               fig.height = 8)
```

```{r load-data, include=FALSE}
tweets <- import(here("data", "rstats_tweets.rds"),
               setclass = "tbl_df") 

head(tweets)


```


# Commit 4
```{r commit 4}

a <- tweets %>%
mutate(month = lubridate::round_date(created_at, unit = "month")) %>% 
  count(month) %>% 
  filter(month < lubridate::as_datetime("2019-01-01 00:00:00"))

ggplot(a, aes(month, n)) +
  geom_line() +
  geom_smooth()

```


# Commit 5
```{r}
ggplot(a, aes(month, n)) +
  geom_line() +
  geom_smooth(color = "pink") +
  geom_area(fill = "skyblue")+
  labs(x = "Year (data summarized by month)", 
       y = "Number of #rstats twitters",
       title = "Growth of the #rstats hashtag on twitter over time",
       caption = "Data from Mike Keamy, distributed via #tidytuesday")


ggplot(a, aes(month, n)) +
  geom_line(color = "gray40") +
  geom_smooth(color = "magenta", se = FALSE) +
  geom_area(fill = "skyblue", alpha = 0.7) +
  labs(x = "Year (data summarized by month)", 
       y = "Number of #rstats twitters",
       title = "Growth of the #rstats hashtag on twitter over time",
       caption = "Data from Mike Keamy, distributed via #tidytuesday")
```

>>>>>>> Stashed changes
